---
title: "EDS212 Day 2 Part 1- Drivatives and git intro"
author: "Kristine Duarte"
date: "2022-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Derivatives in R

Find the Derivitive of $f(x) = 5x^2$

this stuff above is in Latex (different language)

```{r}
ex_1 <- expression (5 * x ^ 2)

my_derivative <- deriv(ex_1, "x")
my_derivative

# I want to find the slope at x = 2.8

x <- 2.8
eval(my_derivative)

# a Word followed by a parentheses is a function
```

Find the slope of $f(x) = 2z^3-10.5z^2+4.1$

```{r}
gz <- expression(2 * z ^ 3 - 10.5 * z ^ 2 + 4.1)

dg_dz <- D(gz, "z")
dg_dz

#Let's evaluate the slope over a range of values

z<- seq(from = -3, to = 4, by = 0.5)

#Evaluate it!
eval(dg_dz)

```

Some awesome text! this is my first file that is going to github Saving on computer- there is baby level of security- to make sure there is a history of changes made, send changes to the local gitrepo

Need to create the git repo every time for projects you want to save version control Click stage box- to send to local git repo (still on local computer- then hit commit) Only shows up when it has been modified and not committed yet.\
Need to send the committed chnages (only locally) need to #PUSH them (green up arrow)

To change default branch (from master b/c of racist connotation) usethis::git_default_branch_rename() automatically assumes you want to change branch name from master to main

Branches to work in- not making changes directly to the core of where things are safely stored until you are ready to push them to the main group